### 2019-06-11 drafts/3points-ellipse5.tex
wip

	\begin{align*}
	A\alpha^2h^2 + B\alpha^2 h^2 m + Cm^2\alpha^2h^2 -Ah^2 \alpha + E m \alpha h = 0\\
	Em = -(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)
	\end{align*}

>>>>

	\begin{align*}
	A\alpha^2h^2 + B\alpha^2 h^2 m + Cm^2\alpha^2h^2 -Ah^2 \alpha + E m \alpha h = 0\\
	Em = -(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)\\
	Em = h(-A(\alpha  - 1) +\alpha m - Cm^2\alpha)\\
	E = h\beta
	\end{align*}

	\subsection{Semi-major}

	Fixando $A$ e utilizando a formula do semi-major, fazendo $H=\Delta(A + C - \sqrt{1 + (A-C)^2})$.

	\begin{align*}
	a^2 H = AE^2 + DE + CD^2\\
	a^2H = Ah^2\beta^2 -Ah^2\beta + CA^2h^2\\
	h^2(A\beta^2 - A\beta + CA^2) = a^2H\\
	h^2 = \frac{a^2H}{A\beta^2 - A\beta + CA^2}
	\end{align*}
